Sex, education, and mental health: Analyzing American census data through statistical methods, 2018 to 2021

### 2024-10-26 paper/paper.qmd
Adds Erickson and Kessler citations to the introduction and fixes a couple of minor typos.

Mental health issues, particularly depression, have emerged as a significant public health concern globally. Among other factors influencing mental health, gender and education stand out as critical determinants. Recent studies have also indicated that educational attainment may play a protective role against depression, suggesting that individuals with higher education levels experience lower rates of mental health issues. Conversely, gender disparities in depression prevalence remain pronounced, with research consistently showing that women report higher rates of depression than their male counterparts, even when controlling for education levels.

@@

## Overview
We used the Medical Expenditure Panel Survey(MEPS) dataset from the Integrated Public Use Microdata Series, which contains microdata from different time points related to U.S. healthcare expenditures [@blewett_ipums_2023]. We performed all analysis using a popular statistical language called R [@citeR]. Our dataset contains age, sex, marital status, race, highest level of education attainment, total personal income, and K6 score [@kessler_kessler_2012].All the variable definitions can be found in the Appendix [-@sec-appendix-data-details].

>>>>

Mental health issues, particularly depression, have emerged as a significant public health concern globally. Among other factors influencing mental health, gender and education stand out as critical determinants. Studies have also indicated that educational attainment may play a protective role against depression, suggesting that individuals with higher education levels experience lower rates of mental health issues [@erickson2016]. Conversely, gender disparities in depression prevalence remain pronounced, with research consistently showing that women report higher rates of depression than their male counterparts, even when controlling for education levels [@kessler2006epidemiology].

@@

## Overview
We used the Medical Expenditure Panel Survey (MEPS) dataset from the Integrated Public Use Microdata Series, which contains microdata from different time points related to U.S. healthcare expenditures [@blewett_ipums_2023]. We performed all analysis using a popular statistical language called R [@citeR]. Our dataset contains age, sex, marital status, race, highest level of education attainment, total personal income, and K6 score [@kessler_kessler_2012]. All the variable definitions can be found in the Appendix [-@sec-appendix-data-details].
